\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems. Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon. The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law). More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).

\medskip
In viscous fingering, a less viscous fluid pushes a more viscous fluid, in a thin rectangular cell (known as Hele-Shaw cell). \citet{howison_2000}  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers. For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape. In heterogeneous environments this process may also be triggered by permeability differences between smaller regions. The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be. In addition, pressure differences %(eq.\ref{eq:pressure_dif}) 
acting on the interface will produce a net pressure force,

>>>>

Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields. Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon\red{(SENTENCE SEEMS INCOMPLETE ... WHAT WERE THE CONTRIBUTION OF THESE AUTHORS ???)}.

\medskip
In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ... SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN? ... TRY TO REWRITE THE SENTENCE)}. More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem). Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.

\medskip
 During the displacement of a fluid by a less viscous one, the expected uniform front is broken \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with long extensions of the fluids (Fig.~\ref{fig:simple_case}), often referred as 'fingers'. In such viscous fluid instabilities, a less viscous fluid displaces a more viscous fluid For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape. In heterogeneous environments this process may also be triggered by permeability differences between smaller regions. The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be. In addition, pressure differences %(eq.\ref{eq:pressure_dif}) 
acting on the interface will produce a net pressure force,
